European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-12 manuscript/manuscript.qmd
future research: 2nd

Second, extending our analysis to include other potential great power influencers—particularly China, whose economic weight and IMF membership have grown substantially since our sample period—would help assess whether the patterns we document reflect specifically transatlantic dynamics or broader features of great power competition within international organisations.

>>>>

A second line of inquiry would be to examine the domestic sources of IMF influence. Our study measures international alignment, but the national actors transmitting influence remain a black box. Case studies focusing on finance ministries, central banks, foreign ministries, or private banking interests could shed light on which domestic constituencies mobilise influence within the IMF, and whether these channels differ between Europe and the United States.
